\documentclass{article}

\begin{document}
\title{Report on Gamestation operation in Kampala}
\author{Kalanda Dico 215005312  15/U/5548/EVE}
\maketitle{}

\section{Introduction}
As a subject of my data collection I collected operation data on different gamestations located in different areas of Kampala City. The purpose was to find out how they operate and find out ways to improve on their services and diversify their businesses.

\section{Procedure}
We collecting the different information by physically going to the gamestations and interviewing their different managers. English and Luganda where the the langueges used during the interviews.

\section{Overall View}
Generally, these stations are located in residential areas and around university areas since these are the areas that provide customers. A few are located in the middle of the city and these provide more services like selling, repairs and maintenance to customers. Prices range from ugshs 2000 for 30 minutes of play and ugshs 4000 for an hour. The most popular game if football specifically Fifa and a few playing PES. The most common platforms are the Playstation 4 and the Xbox one.

\section{Policy used}
The policy used in these station is first come first serve. New customers have to wait for the occupied spaces to be free and then they get to use them too.

\section{Conclusion}
In conclusion these gamestations are mostly up to date in terms of the systems they use and the games they offer to the public though most of them need to improve one the environment in which they operate as most of them are most of the time crowded.

\end{document}